### 2019-11-21 3_implementation.tex
minior edits on ompss
Edits.

\subsection{OmpSs/OpenMP}

OmpSs~\cite{OmpSs11} is a programming model for loop- and task-based parallelism
that is source-compatible with OpenMP. Our Task Bench implementation
uses OpenMP 4.0-style~\cite{OpenMPSpec40} task dependencies. 
Because OpenMP tasks have a fixed number of dependencies, we use a switch
statement to implement the dynamic dependencies required for Task
Bench. The implementation is otherwise straightforward. 
The Task Bench implementation for OpenMP is similar to OmpSs.
We tested with GNU GOMP and Intel KMP and found KMP to be better performing.

>>>>

\subsection{OmpSs and OpenMP}

OmpSs~\cite{OmpSs11} and OpenMP~\cite{OpenMPSpec40} are programming
models for loop- and task-based parallelism. (OmpSs is
source-compatible with OpenMP.) The implementations use OpenMP 4.0
task dependencies.  Because tasks have a fixed number of dependencies,
we use a switch statement to implement dynamic dependencies for Task
Bench. The implementations are otherwise straightforward.  For OpenMP,
we tested GNU GOMP and Intel KMP and found KMP to be better
performing.
